### 2016-11-21 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated figures based on JH + Nelson edits

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Flows}
	\caption[Spray Density Nozzle Patterns]{Spray Density Nozzle Patterns (Left-To-Right: Straight Stream, Narrow Fog Stream, and Solid Stream)}
	\label{fig:Spray_Density_Nozzle_Patterns}
\end{figure}

@@

The burn building, or live fire training structure, contained a two-story section and a three-story section. The building was supported with reinforced concrete beams and columns. The floors and ceilings were also concrete, and the interior walls were constructed of cement block. The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile. The floors of the burn rooms were protected with fire brick. Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
	\caption{Dimensioned Floor Plan Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer. The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft). The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).  The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide. The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide. A dimensioned, plan view of the structure is included in Figure~\ref{fig:Test_Structure_Floor_Plan}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Dimensioned Floor Plan of the Test Structure}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCo}
	\caption{Delaware County, PA Fire Two-Story Test Structure}
	\label{fig:delco_2story}
\end{figure}

The outer walls of the bottom floor of the two-story structure were identical to that of the single-story structures described above but with an open floor plan. The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. Figure~\ref{fig:dimensioned_first_2story} shows the dimensions of the reconfigured first floor. A stairwell was built to connect the floors. Stairs started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall. The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs. The studs were set to 0.40~m (16~in) centers. The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding. Figure~\ref{fig:dimensioned_second_2story} shows the dimensions of the second story of the modified west structure.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Dimensioned Floor Plan of First Floor of Two-Story Structure}
	\label{fig:dimensioned_first_2story}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Dimensioned Floor Plan of Second Floor of Two-Story Structure}
	\label{fig:dimensioned_second_2story}
\end{figure}

@@

The gas cooling tests included four bare-bead thermocouple arrays, a bi-directional probe with a thermocouple array, and a total heat flux gauge/radiometer pair. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the sensors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead thermocouple arrays had 11 thermocouples. The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10ft) below the ceiling. There were 6 velocity probes and solid thermocouples centered at the external doorway to the gas cooling room. The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft) below the soffit, and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit. The total heat flux gauge/radiometer set were positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.

@@

The fire suppression testing in the single-story structure included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux gauge/radiometer pairs. Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each bare-bead thermocouple array had 8 thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe arrays had unique sensor locations. For the window array, there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit. For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling. The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit. The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit. The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical at the ceiling and the other horizontal.

@@

Fire suppression testing in the two-story structure included similar types of instrumentation but included more sensors. Three bare-bead thermocouple arrays and 2 bi-directional probe and thermocouples arrays were used in the first floor. Figure~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests. The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.

@@

The second story featured six bare-bead arrays and three bi-directional probe plus solid thermocouple arrays. The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground. Figure~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level. The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level. The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.

@@

There are different components of uncertainty in the length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$ a) is essentially 100~\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).  For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

Each length measurement was taken carefully. Length measurements, such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement, were made with a hand held laser measurement device that had an accuracy of $\pm$ 6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$ 0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.  Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within an instrumentation array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$ 1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$ 1.0~\%.

The load cell used to weigh the fuels prior to the experiments had a range of 0~kg (0~lb) to 200~kg (440~lb) with a resolution of a 0.05~kg (0.11~lb) and a calibration uncertainty within 1~\%~\cite{Ohaus:2000}. The expanded uncertainty is estimated to be less than $\pm$ 5~\%.

The standard uncertainty in temperature of the thermocouple wire itself is $\pm$ 2.2 $^{\circ}$C at 277 $^{\circ}$C and increases to $\pm$ 9.5~$^{\circ}$C at 871~$^{\circ}$C as determined by the wire manufacturer\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$ 15~\%.

In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges. The manufacturer reports a $\pm$ 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$ 8~\%~\cite{Pitts:2006}.

The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$ 12~\% was applied to the results~\cite{Lock:1}.

Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated and the zero and span of each were checked in the laboratory prior to the experiments, yielding an accuracy of $\pm$ 1~\%~\cite{Setra:2002}. The total expanded uncertainty is estimated at 10~\%.

Bi-directional probes and single thermocouples were used to measure gas velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. Bare-bead Type K thermocouples are co-located with each probe. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm$ 18~\%.

Water flow rate was measured with a pressure and flow meter combination. The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.  The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty is estimated at $\pm$ 10~\%.

@@

The fuel load for test numbers 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets of plywood on the walls, and the wood ``floor assembly''. Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay layered between the six pallets. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed prior to each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).

\begin{figure}[!ht]
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
	\caption{Photograph of Southeast Corner of Burn Room with Wood Fuel Load}
	\label{fig:Wood_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load in Single-Story Structure}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
	\caption{Furniture Fuel Load in First Floor of Two-Story Structure}
	\label{fig:furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure}
	\label{fig:pallet_furniture_2story}
\end{figure}

@@

The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building. For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}. While Mitchell examined each individual experiment in detail, the results were mixed.  In the different gas cooling scenarios, CAF showed slightly better or slightly worse than plain water.  Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3). This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.  As a result, it remained dry and seems to provide the best representation of the gas cooling.

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Flows}
	\caption[Spray Density Nozzle Patterns]{Spray Density Nozzle Patterns. Left-To-Right: Straight Stream, Narrow Fog Stream, and Solid Stream.}
	\label{fig:Spray_Density_Nozzle_Patterns}
\end{figure}

@@

The burn building, or live fire training structure, contained a two-story section and a three-story section. The building was supported with reinforced concrete beams and columns. The floors and ceilings were also concrete, and the interior walls were constructed of cement block. The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile. The floors of the burn rooms were protected with fire brick. Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft). Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
	\caption{Basic Floor Plan of the Burn Building Layout}
	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
\end{figure}

@@

Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer. The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft). The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).  The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide. The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide. A basic plan view of the structure is presented in Figure~\ref{fig:Test_Structure_Floor_Plan}, and a fully dimensioned plan view of the structure is included in in Appendix~\ref{app:floor_plans}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
	\caption{Basic Floor Plan of the Single-Story Test Structure}
	\label{fig:Test_Structure_Floor_Plan}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCo}
	\caption{Delaware County, PA Two-Story Fire Test Structure}
	\label{fig:delco_2story}
\end{figure}

The outer walls of the bottom floor of the two-story structure were identical to that of the single-story structures described above but with an open floor plan. The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high. Figure~\ref{fig:dimensioned_first_2story} shows a basic floor plan of the reconfigured first floor. A fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}. A stairwell was built to connect the two floors of the structure. The stairs had a 180~mm (7.25~in) rise and 190~mm (7.5~in) run and started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall. The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs. The studs were set to 0.40~m (16~in) centers. The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board. The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding. Figure~\ref{fig:dimensioned_second_2story} shows a basic floor plan of the second story of the modified west structure, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
	\caption{Basic Floor Plan of the First Floor of the Two-Story Structure}
	\label{fig:dimensioned_first_2story}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
	\caption{Basic Floor Plan of the Second Floor of the Two-Story Structure}
	\label{fig:dimensioned_second_2story}
\end{figure}

@@

The gas cooling tests included four bare-bead thermocouple arrays, a bi-directional probe with a thermocouple array, and a total heat flux gauge/radiometer pair. Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the sensors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead thermocouple arrays had 11 thermocouples. The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10~ft) below the ceiling. There were six velocity probes and solid thermocouples centered at the external doorway to the gas cooling room. The top probe was 0.15~m (0.5~ft) below the door soffit, the second probe was 0.3~m (1~ft) below the soffit, and the remaining four were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit. The total heat flux gauge/radiometer set was positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.

@@

The fire suppression testing in the single-story structure included two bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, two total heat flux gauge pairs, and two total heat flux gauge/radiometer pairs. Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the sensors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each bare-bead thermocouple array had eight thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. The three bi-directional probe arrays had unique sensor locations. For the window array, there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit. For the hallway array, the seven sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling. The doorway array also had seven sensor pairs, but the first pair was located 0.15~m (0.5~ft) below the soffit. The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit. The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical at the ceiling and the other horizontal.

@@

Fire suppression testing in the two-story structure included similar types of instrumentation but with more sensors. Three bare-bead thermocouple arrays and two bi-directional probe and thermocouple arrays were used in the first floor. Figure~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). Each of the bare-bead arrays had eight thermocouples with the same spacing as the single-story tests. The bi-directional probe and solid thermocouple arrays also had eight sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.

@@

The second story featured six bare-bead arrays and three bi-directional probe plus solid thermocouple arrays. The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground. Figure~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols). The bare-bead thermocouple arrays featured eight sensors with the same spacing as the basement level. The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of eight sensor pairs with the same spacing as the ground level. The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) had eight sensor pairs with the same spacing at the bare-bead thermocouple arrays.

@@

There are different components of uncertainty in the length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate reported here. Uncertainties are grouped into two categories according to the method used to estimate them. Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}. Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$~a) is essentially 100~\%. After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty. Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).  For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications. For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.

Each length measurement was taken carefully. Length measurements, such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement, were made with a hand held laser measurement device that had an accuracy of $\pm$~6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}. However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$~0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.  Steel measuring tapes with a resolution of  $\pm$~0.5~mm (0.02~in) were used to locate individual sensors within an instrumentation array and to measure and position the furniture. The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$~1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$~6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}. Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$~1.0~\%.

The load cell used to weigh the fuels prior to the experiments had a range of 0~kg (0~lb) to 200~kg (440~lb) with a resolution of a 0.05~kg (0.11~lb) and a calibration uncertainty within 1~\%~\cite{Ohaus:2000}. The expanded uncertainty is estimated to be less than $\pm$~5~\%.

The standard uncertainty in temperature of the thermocouple wire itself is $\pm$~2.2~$^{\circ}$C at 277~$^{\circ}$C and increases to $\pm$~9.5~$^{\circ}$C at 871~$^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used to limit the impact of radiative heating and cooling. The estimated total expanded uncertainty for temperature in these experiments is $\pm$~15~\%.

In this study, total heat flux measurements were made with water-cooled Schmidt-Boelter gauges. The manufacturer reports a $\pm$~3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$~8~\%~\cite{Pitts:2006}.

The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k~=~2) relative uncertainty of $\pm$~1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$~12~\% was applied to the results~\cite{Lock:1}.

Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers. The transducers were factory calibrated and the zero and span of each were checked in the laboratory prior to the experiments, yielding an accuracy of $\pm$~1~\%~\cite{Setra:2002}. The total expanded uncertainty is estimated as $\pm$~10~\%.

Bi-directional probes and single thermocouples were used to measure gas velocity. The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above. Bare-bead Type K thermocouples are co-located with each probe. A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$~0.14 to $\pm$~0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}. The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm$~18~\%.

Water flow rate was measured with a pressure and flow meter combination. The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.  The manufacturer reports a $\pm$~5~\% calibration expanded uncertainty for the flow sensor and $\pm$~3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate. The total expanded uncertainty is estimated at $\pm$~10~\%.

@@

The fuel load for test numbers 9 through 12 consisted of one bale of hay, 12 pallets, 11.5 sheets of plywood on the walls, and the wood ``floor assembly''. Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay layered between the six pallets. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed before each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).

\begin{figure}[!ht]
	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
	\caption{Southeast Corner of Burn Room with Wood Fuel Load}
	\label{fig:Wood_Fuel_Load}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
	\caption{Wood Fuel Load Dimensions in Single-Story Structure}
	\label{fig:Wood_Fuel_Load_Dimensions}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
	\caption{Furniture Fuel Load Dimensions in First Floor of Two-Story Structure}
	\label{fig:furniture_2story}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
	\caption{Furniture and Pallet Fuel Load Dimensions in First Floor of Two-Story Structure}
	\label{fig:pallet_furniture_2story}
\end{figure}

@@

The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building. For detailed discussion on each of the individual events, refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}. While Mitchell examined each individual experiment in detail, the results were mixed. In the different gas cooling scenarios, CAF showed slightly better or slightly worse than plain water. Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.

@@

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used. The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3). This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 also exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.  As a result, it remained dry and seems to provide the best representation of the gas cooling.   
`'
\begin{figure}[ht!]
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent}
	\label{fig:gas_cooling_sub1}
\end{figure}
